
\documentclass{article} % For LaTeX2e
\usepackage{iclr2024,times}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
% \input{math_commands.tex}
\usepackage[backgroundcolor=white, textsize=small, textwidth=20mm, disable]{todonotes}
\usepackage{proj}

\usepackage{wrapfig}
\newtheorem{observation}[theorem]{Observation}

\title{Goodhart's Law in Reinforcement Learning}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.


\author{Jacek Karwowski\\
Department of Computer Science\\
University of Oxford\\
\texttt{jacek.karwowski@cs.ox.ac.uk}
\And
Oliver Hayman\\
Department of Computer Science\\
University of Oxford\\
\texttt{oliver.hayman@linacre.ox.ac.uk}
\And
Xingjian Bai\\
Department of Computer Science\\
University of Oxford\\
\texttt{xingjian.bai@sjc.ox.ac.uk}
\And
Klaus Kiendlhofer\\
Independent\\
\texttt{klaus.kiendlhofer@gmail.com}
\And
Charlie Griffin\\
Department of Computer Science\\
University of Oxford\\
\texttt{charlie.griffin@cs.ox.ac.uk}
\And
Joar Skalse\\
Department of Computer Science\\
Future of Humanity Institute\\
University of Oxford\\
\texttt{joar.skalse@cs.ox.ac.uk}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle


\begin{abstract}
Implementing a reward function that perfectly captures a complex task in the real world is impractical. As a result, it is often appropriate to think of the reward function as a \emph{proxy} for the true objective rather than as its definition. We study this phenomenon through the lens of \emph{Goodhart’s law}, which predicts that increasing optimisation of an imperfect proxy beyond some critical point decreases performance on the true objective. First, we propose a way to \emph{quantify} the magnitude of this effect and \emph{show empirically} that optimising an imperfect proxy reward often leads to the behaviour predicted by Goodhart’s law for a wide range of environments and reward functions. We then provide a \emph{geometric explanation} for why Goodhart's law occurs in Markov decision processes. We use these theoretical insights to propose an \emph{optimal early stopping method} that provably avoids the aforementioned pitfall and derive theoretical \emph{regret bounds} for this method. Moreover, we derive a training method that maximises worst-case reward, for the setting where there is uncertainty about the true reward function. Finally, we evaluate our early stopping method experimentally. Our results support a foundation for a theoretically-principled study of reinforcement learning under reward misspecification.
\end{abstract}


\input{s1-introduction}
\input{s1-2-related_work}
\input{s2-preliminaries}
\input{s3-quantifying_goodharting}
\input{s4-explaining_goodharting}
\input{s5-avoiding_goodharting}
\input{s6-discussion}

\bibliography{export-data} % Entries are in the refs.bib file
\bibliographystyle{iclr2024_conference}

% \input{goodharting_happens/goodharting_happens_appendix}

\appendix

% the first one is "include" to get a newpage
\include{appendix/intuitive_explanation_appendix}
\include{appendix/proof_appendix}
\include{appendix/quantifying_goodharting_appendix}
\include{appendix/evaluation_appendix}
\include{appendix/example_appendix}
\include{appendix/iterative_improvement_appendix}

\include{appendix/further_results}
\include{appendix/experiment_details}
\include{appendix/example3d_appendix}

\end{document}